preciseTAD: A machine learning framework for precise TAD boundary prediction at base-level resolution

### 2020-08-27 Manuscript/manuscript.Rmd
Revert Figure 6 legend
Fog 6: Jaccard reflects whole genome overlap

![**preciseTAD-predicted boundaries are both statistically significantly closer to CTCF sites and more conserved across cell lines**. (A) Log2 genomic distances from called and predicted boundaries to nearest CTCF sites. P-value are from the Wilcoxon Rank Sum test. (B) Venn diagrams illustrating the levels of conservation between domain boundaries for GM12878 (red) and K562 (blue) cell lines identified by Arrowhead-trained *preciseTAD* model (top left), Arrowhead boundaries themselves (top right), Peakachu-trained *preciseTAD* model (bottom left), and Peakachu boundaries themselves (bottom right). J - the median Jaccard Index (IQR in parentheses) across all chromosomes.](Figures/figure6.png)

>>>>

![**preciseTAD-predicted boundaries are both statistically significantly closer to CTCF sites and more conserved across cell lines**. (A) Log2 genomic distances from called and predicted boundaries to nearest CTCF sites. The p-values are from the Wilcoxon Rank Sum test. (B) Venn diagrams illustrating the levels of conservation between domain boundaries for GM12878 (red) and K562 (blue) cell lines identified by Arrowhead-trained *preciseTAD* model (top left), Arrowhead boundaries themselves (top right), Peakachu-trained *preciseTAD* model (bottom left), and Peakachu boundaries themselves (bottom right). J - the Jaccard Index evaluating the similarity between each set of boundaries flanked by resolution.](Figures/figure6.png)
